Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
added emails to draft, fixed grammar, added pdf

\title{Combined Task and Motion Planner through an Interface Layer}
\author{Alex Gutierrez, Bianca Homberg, and Veronica Lane}

@@

\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/walkthrough.pdf_tex}
\caption{Walkthrough Example. The goal was for the red block to be on surface S.\label{fig:walkthrough}}
\end{figure}

@@

The original version of the algorithm, as shown in \ref{fig:algorithms}, only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification where, every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses won't work but others will, so it is in our benefit to try and make the simplest possible plan work before giving up and making the high level plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.

>>>>

\title{Combined Task and Motion Planner through an Interface Layer}
\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), and Veronica Lane (vmlane@mit.edu)}

@@

\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/walkthrough.pdf_tex}
\caption{Walkthrough Example. The goal is for the red block to be on surface S.\label{fig:walkthrough}}
\end{figure}

@@

The original version of the algorithm, as shown in (Fig. \ref{fig:algorithms}), only attempts to find partial trajectories when it replans partway through the procedure.  Our algorithm has a slight modification. Every time a new partial plan is generated, we first try to fill it completely using backtracking search before giving up and resorting to the partial trajectory finding.  In some scenarios, some poses will not work but others will, so it is better to try to make the simplest possible plan work before giving up and making the high level plan more complicated.  In our manipulation example, this turns into trying to pick up blocks from all angles before giving up and assuming they must be blocked by something.  An analysis of the benefits of this approach are outlined in the benchmarking section.
